### 2014-04-16 doc/uist14/iteration3.tex

In the first stage, the user orients their head towards each device, and the
system learns a map of the devices based on their corresponding sensor readings.
During the second stage, when the user wishes to use head-motion for
disambiguation, they will put their finger on the touchpad to enter a
quasi-mode, where only one device has a solid indicator light on at a time. This
gesture is inspired by observing users who tend to adjust their glasses for
closer inspection. The user can then tilt in the direction of the device they
wish to switch to. The system then uses its understanding of the relative
locations of the devices to create an {\em adjacency map}.

The technical implementation of this interaction involves a number of subtleties
due to the noisiness of our data. As mentioned earlier, absolute orientations
of devices change frequently at the slightest user movement. Unfortunately,
while relative orientation information is more stable, it does not contain
the necessary information for essential tasks, such as adding devices to a
learned map. To overcome these issues, we implement a hybrid method using
absolute and relative orientations augmented by IR information. Our system
stores the absolute orientations of each device during the learning stage, but
utilizes only the relative information for disambiguation. Once the user is in
quasi-mode, our system calculates the user's direction of motion using a
low-passed history of sensor measurements, and searches through the devices for
the nearest device in that direction. Thus, although the absolute orientations
may be incorrect, the relative information can still be used for disambiguation.

>>>>

In the learning stage, the user scans over the targets, and the
system attains the absolute orientation of each device from IR and motion sensors. From this information it can abstract out their relative positions and build an {\em adjacency map}.

After the map is created, the user can hold down on the touchpad to enter a
quasi-mode for refinement. In this quasi-mode, one device lights up at a time. When the user turns his head in the direction of another device, the light switches to that device. Therefore, the user can move between devices one at a time with slight head movements. We implement this interaction by calculating the user's direction of motion using a low-passed history of sensor measurements and searching through the adjacency map for
the nearest device in that direction.
